%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

\newcommand{\classesList}[4]{
	\item\small{
		{#1 #2 #3 #4 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textbf{\small #2} \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\item
	\begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & \textbf{\small #2}\\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	
	%----------HEADING----------
	% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
	%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
	% \end{tabular*}
	
	\begin{center}
		{\Huge \scshape Indra Yanto} %\\ %\vspace{1pt}
	%Jl. Cisitu Indah V No. 8 Bandung, Indonesia 
	\\ \vspace{2pt}
		\small \href{https://indrayantom.github.io/indrapedia/}{\raisebox{-0.2\height}\faGlobe\ Personal Website} ~ \href{mailto:iyanto201199@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  iyanto201199@gmail.com} ~ \raisebox{-0.1\height}\faPhone (+62)823-6486-3157 \\
		\href{https://www.linkedin.com/in/indrayantom/}{\raisebox{-0.2\height}\faLinkedin\ linkedin.com/in/indrayantom}  ~
		\href{https://github.com/indrayantom}{\raisebox{-0.2\height}\faGithub\ github.com/indrayantom}
		\vspace{-8pt}
	\end{center} 
	\vspace{7pt}
	
	Conscious and creative Data Scientist with 2+ years of experience and a diverse set of projects to offer. Proficient in statistics, machine learning modeling, data pipeline design, and scripting programming languages including Python, R, and Matlab. Capable of translating business problems into statistical or mathematical model and bundling them into significant deliverables that drive corporate growth.	
	%-----------EDUCATION-----------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{dibimbing.id}{October 2021 -- March 2022}
	{Non- formal Education of Data Science and Analyst}{Online}
		\resumeItemListStart
	\resumeItem{Composed numerous projects, related to machine learning problems (classification, regression, and clustering), data analysis, data visualization or dashboard making, and SQL queries, based on Kaggle and open-source datasets.}
	\resumeItem{Graduated with the highest grade among the class members, and won the "Most Valuable Person" and "Best Final Project" awards.}
	\resumeItemListEnd
	\resumeSubheading
	{Institut Teknologi Bandung}{August 2017 -- October 2021}
	{Bachelor of Science in Aerospace \& Aeronautical Engineering}{Bandung, Indonesia}
	\resumeItemListStart
	\resumeItem{Graduated with a cumulative GPA  of 3.87/4.00. }
	\resumeItem{The Awardee of Samosir Regency Scholarship 2020.}
	\resumeItem{Dean's List of Tutor Asrama ITB 2020.}
	\resumeItem{The Winner of DIY Soap-Box Car Race Project 2017 held by FTMD ITB.}
	\resumeItemListEnd
	\resumeSubHeadingListEnd
	
	%------RELEVANT COURSEWORK-------
%	\section{Relevant Coursework}
	%\resumeSubHeadingListStart
%	\begin{multicols}{4}
%		\begin{itemize}[itemsep=-5pt, parsep=3pt]
%			\item\small Data Structures
%			\item Software Methodology
%			\item Algorithms Analysis
%			\item Database Management
%			\item Artificial Intelligence
%			\item Internet Technology
%			\item Systems Programming
%			\item Computer Architecture
%		\end{itemize}
%	\end{multicols}
%	\vspace*{2.0\multicolsep}
	%\resumeSubHeadingListEnd
	
	
	%-----------EXPERIENCE-----------
	\section{Professional Experiences}
	\resumeSubHeadingListStart

	\resumeSubheading
	{AgriAku}{May 2022 -- July 2022}
	{Full-time Data Scientist (Hybrid)}{Jakarta, Indonesia}
	\resumeItemListStart
	\resumeItem{Developed a content-based (item similarity) recommendation model for agricultural items (pesticide, fertilizer, seed, etc.) across all brands using the Graph Algorithm. Subsequently, the recommender was integrated into an internal web application, enabling the sales team and other teams to quickly and precisely compile a list of substitutes for any agricultural items (SKU). }
	\resumeItem{Conducted Causal Inference analysis to determine whether the recently-launched pay-later campaign had significant improvements in terms of customer's spending behavior. By implementing the Difference-in-Difference approach as well as the Placebo test, the analysis concluded that the campaign had significant impact on driving the customer to be more consumptive.}
	\resumeItem{Built a KYC Fraud Detection system using Deep Learning with Siamese-DenseNet architecture that runs daily. After the final tuning, the outcome showed an 75\% of recall and 10\% precision. Implying that 75\% of frauds should be found requiring 70\% less data to be examined.}
	\resumeItem{Conducted feature engineering about customer in-app behavior using Gradient-Boosted Decision Tree and loaded it into a daily-updated reverse ETL pipeline for a deep collaborative filtering-based recommender system model, called BB8Net. By alone, this model is able to produce a list of recommended products, of which 60\% of customers that transacted on that particular period purchased at least one from the top ten items. And after being enhanced by Product Seasonality and Google's deep collaborative filtering-based recommendation model called Wide and Deep, the results appear to be better in terms of performance metrics, with an accuracy of 88\% and an F1-score of 93\%.}
	\resumeItem{Designed and created an internal web-app by using Python (Holoviz Panel) that allows the logistics team to automatically discover the ideal location of Hubs and Collection Points based on Weighted Clustering algorithm.}
	\resumeItem{Implemented a weighted clustering to identify the ideal position of pre-determined number of logistics hubs in a given area, and vehicle routing problem to estimate the total delivery distance for the logistics fleet, as well as linear programming to generate the most ideal and efficient fleet arrangement based on both results : In Jawa Barat (West Java), it is found that 6 logistics hubs proves to be the most optimal arrangements with an estimated benefit-cost ratio of 1.5\% with 3 days SLA. These hubs were then installed in the region during the very next month.}
	\resumeItem{Applied LRFM theory to create a customer segmentation model and integrated it into a daily updated reverse ETL pipeline. This segmentation proves to be essential as it enables the creation of more individualized marketing strategies and actions.}
	\resumeItem{Utilized conjoint analysis to understand the influence of seller location, ratings, and product's pricing on the customer's decision to choose their preferred product.}
	\resumeItemListEnd

	\newpage 
	
	\resumeSubheading
	{FlavorWiki}{May 2022 -- July 2022}
	{Full-time Junior Data Scientist (Remote)}{Zurich, Switzerland}
	\resumeItemListStart
	\resumeItem{Designed and developed a dashboard using Python and Google Data Studio to track the completion progress of ongoing surveys.}
	\resumeItem{Evaluated the completed surveys using statistical techniques such as conjoint method, clustering analysis, and post-hoc difference test, and provided the results to the clients via presentation decks.}
	\resumeItemListEnd
	
	\resumeSubheading
	{PT. Aero Terra Indonesia (AeroTerrascan)}{February 2021 -- May 2021}
	{UAV Engineer Intern}{Bandung, Indonesia}
	\resumeItemListStart
	\resumeItem{Designed precise mathematical model of Pindad SS2-V2 recoil absorption system with spring and multi-orifices shock absorber using MATLAB and Simulink.}
	\resumeItem{Obtained clear specifications about the recoil absorption system based on the mathematical model so that it can absorb Pindad SS2's recoil energy efficiently and good to be assembled with certain UAV.}
	\resumeItemListEnd
	
	\resumeSubheading
	{UPT Asrama ITB}{July 2018 -- July 2020}
	{Student Counselor -- Calculus Tutor -- Lecturer Assistant}{Bandung, Indonesia}
	\resumeItemListStart
	\resumeItem{Collaborated with the lecturers to assist, help and encourage freshman students in ITB dormitory in order to help them through their college first-year journey.}
	\resumeItem{Guided and supervised a group of 8-12 freshman ITB students as their dorm parent.}
	\resumeItem{Helped first-year ITB dorm students understand their calculus subject better at college by conducting calculus tutorial classes and Tryouts.}
	\resumeItem{Assisted the lecturer in dormitory special subject at ITB, namely Pendidikan Karakter (Character Building).}
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	\vspace{-16pt}
	
	%-----------EXPERIENCE-----------
	\section{Organizational Experiences}
	\resumeSubHeadingListStart
	
	\resumeSubheading
	{Keluarga Mahasiswa Teknik Penerbangan (KMPN) ITB}{August 2018 -- October 2021}
	{Regular Member -- Staff of REKON Division}{Bandung, Indonesia}
	\resumeItemListStart
	\resumeItem{Contributed to the success of KMPN's major event SONIC 2019 (Study of Organization and Creativity) as Head of Logistics Division}
	\resumeItem{Participated in KMPN's Graduation Ceremony as Staff of Logisitics Division in July 2019.}
	\resumeItem{Enlighted other members of KMPN about the latest news and innovations related to the aviation world by conducting seminars and writing Medium articles.}
	\resumeItemListEnd
	
	\resumeSubheading
	{Perkumpulan Mahasiswa Penerbangan Indonesia (PN INDO - Bandung)}{August 2020 -- August 2021}
	{Staff of Academic Division}{Bandung, Indonesia}
	\resumeItemListStart
	\resumeItem{Collaborated with the team to the success of PN-INDO events such as seminars, company visits and scientific writing competition called AeroEvent.}
	\resumeItem{Collected free-access files such as scientific journals, books, software and videos related to aviation from all universities so they can be easily accessed by all aviation students in Indonesia through Google Drive platform called Aerofolder.}
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	\vspace{-16pt}

	
	%-----------PROJECTS-----------
%	\section{Organizational Experiences}
%	\vspace{-5pt}
%	\resumeSubHeadingListStart
%	\resumeProjectHeading
%	{\textbf{Keluarga Mahasiswa Teknik Penerbangan (KMPN) ITB} %$|$ \emph{Python, Selenium, Google Cloud Console}
%	}{August 2018 -- October 2021}
%	\resumeItemListStart
%	\resumeItem{Contributed to the success of KMPN's major event SONIC 2019 %(Study of Organization and Creativity) as Head of Logistics Division. }
%	\resumeItem{Participated in KMPN's Graduation Ceremony as Staff of %Logisitics Division in July 2019.}
%	\resumeItem{Enlighted other members of KMPN about the latest news and innovations related to the aviation world by conducting seminars and writing Medium articles, as PWK staff from 2018 - 2019.}
%	\resumeItemListEnd
%	\vspace{-13pt}
%	\resumeProjectHeading
%	{\textbf{Perkumpulan Mahasiswa Penerbangan Indonesia (PN INDO - Bandung)} %$|$ %\emph{Java, Android Studio}
%	}{August 2020 -- August 2021}
%	\resumeItemListStart
%	\resumeItem{Collaborated with the team to the success of PN-INDO events such as seminars, company visits and scientific writing competition called AeroEvent.}
%	\resumeItem{Collected free-access files such as scientific journal, books, softwares and videos related to the aviation from all universites so that it can be freely accessed by all aviation students in Indonesia through Google Drive platform called Aerofolder, as Staff of Academic Division. }
%	\resumeItemListEnd 
%	\vspace{-13pt}
%	\resumeProjectHeading
%	{\textbf{Rumah Ilmu Keluarga Sangkuriang (RIKSA)} $|$ \emph{Java, Eclipse, JavaFX}}{October 2020}
%	\resumeItemListStart
%	\resumeItem{Designed a sample banking transaction system using Java to simulate the common functions of using a bank account.}
%	\resumeItem{Used JavaFX to create a GUI that supports actions such as creating an account, deposit, withdraw, list all acounts, etc.}
%	\resumeItem{Implemented object-oriented programming practices such as inheritance to create different account types and databases.}
%	\resumeItemListEnd 
%	\resumeSubHeadingListEnd
%	\vspace{-15pt}
	
	
	%
	%-----------PROGRAMMING SKILLS-----------
	\section{Languages and Technical Skills}
	\begin{itemize}[leftmargin=0.15in, label={}]
		\small{\item{
				\textbf{Languages}{ : Native Bahasa, professional English, and intermediate German. } \\
				\textbf{Proficient}{ : MATLAB, Python, R (RStudio), Ms. Office, and Google Data Studio.} \\
				\textbf{Intermediate}{ : Tableau,  SQL, HTML, and CorelDRAW.} \\
		}}
	\end{itemize}
	\vspace{-16pt}
	
	
	%-----------INVOLVEMENT---------------
%	\section{Leadership / Extracurricular}
%	\resumeSubHeadingListStart
%	\resumeSubheading{Fraternity}{Spring 2020 -- Present}{President}{University Name}
%	\resumeItemListStart
%	\resumeItem{Achieved a 4 star fraternity ranking by the Office of Fraternity and Sorority Affairs (highest possible ranking).}
%	\resumeItem{Managed executive board of 5 members and ran weekly meetings to oversee progress in essential parts of the chapter.}
%	\resumeItem{Led chapter of 30+ members to work towards goals that improve and promote community service, academics, and unity.}
%	\resumeItemListEnd
	
%	\resumeSubHeadingListEnd
	
	
\end{document}